Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-10-24 doc/prelim/presentation/prelim_presentation.tex
adding pdf files for presentation

%%---------------------------------------------------------------------------%%
\begin{frame}{Stationary Methods}
  General stationary methods are formed by splitting the linear
  operator:
  \[
  \ve{A} = \ve{M} - \ve{N}\:.
  \]

  We can then reformulate the linear system as:
  \[
  \ve{x} = \ve{M}^{-1}\ve{N}\ve{x} + \ve{M}^{-1}\ve{b}\:.
  \]

  We identify $\ve{M}^{-1}\ve{N}$ as the \textit{iteration matrix},
  $\ve{H}$, and apply iteration indices to the solution vectors to
  give an iterative method.
  \[
  \ve{x}^{k+1} = \ve{H}\ve{x}^{k} + \ve{c}\:.
  \]

  The qualities of the iteration matrix dictate convergence. Defining
  $\ve{e}^k = \ve{x}^k-\ve{x}$ as the error at the $k^{th}$ iterate
  gives a recurrence relation:
  \[
  \ve{e}^{k+1} = \ve{H} \ve{e}^k\:,
  \]

>>>>

%%---------------------------------------------------------------------------%%
\begin{frame}{Stationary Methods}

  General stationary methods are formed by splitting the linear
  operator:
  \[
  \ve{A} = \ve{M} - \ve{N}\:.
  \]

  \[
  \ve{x} = \ve{M}^{-1}\ve{N}\ve{x} + \ve{M}^{-1}\ve{b}\:.
  \]

  We identify $\ve{H} =\ve{M}^{-1}\ve{N}$ as the \textit{iteration
    matrix}

  \[
  \ve{x}^{k+1} = \ve{H}\ve{x}^{k} + \ve{c}\:.
  \]

%%---------------------------------------------------------------------------%%
\begin{frame}{Stationary Methods Convergence}

  \begin{itemize}
  \item The qualities of the iteration matrix dictate convergence 
  \item Define $\ve{e}^k = \ve{x}^k-\ve{x}$ as the error at the
    $k^{th}$ iterate
  \item The iteration error is generated by a recurrence relation
  \end{itemize}

  \[
  \ve{e}^{k+1} = \ve{H} \ve{e}^k\:,
  \]
